---
title: "Homework 8"
author: "Arthur Harnisch"
date: "October 15, 2017"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


```

Use the files in the temperature_trials folder, plus the metadata file 'Heating_trial_info.xlsx' to replicate the two plot


Use relative file paths in your .Rmd file, and assume that your .Rmd file resides in a folder like 255E/Week8 while the data files are in 255E/data/ and 255E/data/temperature_trials/

1st Importing data 

```{r dataImport}

#importing the heating trial info xlsx sheet

library(xlsx)
heating = read.xlsx("../data/Heating_trial_info.xlsx", sheetIndex = 1)


#using a pattern and for loop to import multiple temperature trials 

myfiles=dir("../data/temperature_trials", pattern = "*.csv$", all.files = TRUE, full.names = TRUE)


for(i in 1: length(myfiles) ){
  
  #open each file
  read.csv(myfiles[i])
  temp = read.csv(myfiles[i])
 
  temp$DateTime = as.POSIXct(temp$DateTime, origin = '1970-1-1', tz="")
  
  temp$elapsedTime = difftime(temp$DateTime, temp$DateTime[1], units = 'mins') 
 
  temp$elapsedTimeMin = as.numeric(temp$elapsedTime)
 
  
    loc = (regexpr(pattern ="Trial[0-9]*", text = myfiles [i]))


  trialNumber = as.numeric(substr(myfiles[i], start = loc[[1]][1]+5, 
       stop = loc[[1]][1] + attr(loc, 'match.length')-1))
  
  temp$TrialNumber =trialNumber
  
    if ( i == 1){
  res = temp
  } else {
  res = rbind( res, temp)
}
}

res$DateTime = as.POSIXct(res$DateTime, origin = '1970-1-1', tz="")

res$POSIXt = as.POSIXct(res$POSIXt, origin = '1970-1-1', tz='')



```
Subsetting the imported data
```{r subSetdata}

#using elapsed time column until zero and plot, usinh the lines function. you can also append a new column from the import function
#add a line for pull fiel name out and add it to another column. 
# pull out the trial number 

###grab the trial number 

fnames = dir("../data/temperature_trials", 
             pattern = "*.csv", full.names = TRUE)

for (i in 1:length(fnames)){


#allows to add new column



  
  loc = (regexpr(pattern ="Trial[0-9]*", text = fnames [i]))


  trialNumber = as.numeric(substr(fnames[i], start = loc[[1]][1]+5, 
       stop = loc[[1]][1] + attr(loc, 'match.length')-1))
  
  temp$TrialNumber =trialNumber
  
 print(trialNumber)
}



head(heating)

head(res)


#calculate a time for each entry




```

#write a routine to import multiple CSv

# this could be done through, looping data could do this. for (i in 1:){

#} # questions is from one to what. 


make an initial plot then use for loop to add the other trials lines

```{r plotRes}
#TC0~elapsedTime
#data = res[res$trialNumber ==1
#ploting trial 1 use plot command then lines command 

firstTrial =1
plot(x=res$elapsedTimeMin[res$TrialNumber ==1], y= res$TC0[res$TrialNumber == firstTrial],
      
     type = 'l', 
     xlab = 'Elapsed time, Minutes',
     ylab = 'temperature C', las = 1,
xlim  = c(0,max(res$elapsedTime)),
ylim = c(min(res$TC0), max(res$TC0)))

mtext(text = "Channel TC0 for each Trial", side = 3, line =1.4, cex =  1.5, 
adj = 0)

# elapsedTime)),


trialNums = unique(res$TrialNumber)

for(y in 2:length(trialNums) ){
  lines(x = res$elapsedTimeMin[res$TrialNumber == trialNums[y]],
  y=res$TC0[res$TrialNumber == trialNums[y]], col = y)
}


```
Matching and Second plot for temperature data from location In50 for each trial Number. 

```{r matching}

#goal is to make the second plot, we wiil need the trial heating info, we will need to extract the channel, extra in50 for each trial. channel # is located ch0-ch7, # get a channel label, 
library(xlsx)

heatingInfo = read.xlsx("../data/Heating_trial_info.xlsx", sheetIndex = 1)

heatingInfo$TCchannel = as.character(heatingInfo$TCchannel)

chloc = regexpr(pattern = "[[:digit:]]", heatingInfo$TCchannel[2])


chNum = substr(heatingInfo$TCchannel[1], start = chloc[[1]][1], stop = chloc[[1]][1])

chName = paste("TC", chNum, sep = "")


temps = res[ , "TC0"]



####### get the channel number 



#for(x in 1:96){
  

for(x in 1:96)
 if  (heatingInfo$TCLocation[x] == "In50") {
   chloc = regexpr(pattern = "[[:digit:]]", 
                   heatingInfo$TCchannel[x]) 
   chNum = substr(heatingInfo$TCchannel[x], 
                  start = chloc[[1]][1], stop = chloc[[1]][1])
   chName = paste("TC", chNum, sep = "")
   trialNumber = heatingInfo$TrialNumber[x]
   
   temps = res[ res$TrialNumber == trialNumber , chName]
   
  times= res$elapsedTimeMin[res$TrialNumber == trialNumber]

   
  print(x)
  
 plot(x= times, y = temps,
      
     type = 'l', 
     xlab = 'Elapsed time, Minutes',
     ylab = 'temperature C', las = 1,
xlim  = c(0,max(times)),
ylim = c(min(temps), max(temps)))

mtext(text = "Location In50 for each Trial Number", side = 3, line =1.4, cex =  1.5, 
adj = 0)


#commented out line function from class

#trialNums = unique(res$TrialNumber)

#for(y in 2:length(trialNums) ){
  #lines(x = res$elapsedTimeMin[res$TrialNumber == trialNums[y]],
 # y=res$TC0[res$TrialNumber == trialNums[y]], col = y)
#}



#attempt to fix lines funciton for second plot

#trialNum = res$TrialNumber

  #for(y in 2:length(trialNum) ){
  #lines(x = times == trialNum[y]],
 #y=temps, col = y)
}

  
  
  
  #will rpobably need some logic in here to make a plot the first time and then use lines function every time after that. 
 
  
# }


#asked for maximum   max(which(heatingInfo$heatingInfo$trail ==12))


#do not want to go beyond row 12

#get the numeric channel out



##

```




