---
title: "KimThan_Portfolio"
author: "Kimberly Than"
date: "October 25, 2017"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Import data

Here, I would have imported an Excel file that has multiple sheets (control, glutamate, xanthurenic acid at different doses).

```{r importData}
library(xlsx)

df = read.xlsx("../data/MasterGlutamateSpreadsheet.xlsx")
```

## Including plots for over time 

Here, I would include code to plotting line graphs to show effects over time for Final Static Time (FST) and Dynamic Index (DI). 
For each plot, I want to graph 4 line over time where each line is the average of all trials specific to that dose/condition. 
For the DI plot, I need to make a calculation first, where I am subtracting two values (DynamicPeak - InitialStaticTime) and inputing 
those values into a new data frame where I can plot it easily. I want to include error bars for each condition as well as a color using
colorBrewer package. The plot after time 21 minutes will be a different color to denote drug exposure. 

```{r plotOT}
##### plot FST #####

# Perhaps a for loop for taking averages of different "doses"

# avgTCFST = take the average of FST at each time point of all TC trials 

# avgGlu1FST = take the average of FST at each time point of all 1mM glutamate trials
# avgGlu3FST = take the average of FST at each time point of all 3mM glutamate trials
# avgGlu5FST = take the average of FST at each time point of all 5mM glutamate trials 

# avgXA1FST = take the average of FST at each time point of all 1mM xanthurenic acid trials 
# avgXA3FST = take the average of FST at each time point of all 3mM xanthurenic acid trials 
# avgXA10FST = take the average of FST at each time point of all 10mM xanthurenic acid trials 

# Time control vs. Glutamate
# Plot avgTCFST (x = time in minutes, y = instantaneous frequency (%baseline))
# Add error bars of time control
# lines for avgGlu1FST, avgGlu3FST, avgGlu5FST
# Add error bars of each dose

##### plot DI #####

# DynamicIndex = DynamicPeak - InitialStaticTime
# Create new data set for this calculation, grabbing values tagged 'DP' and 'IST'

# avgTCDI = take the average of DI at each time point of all TC trials 

# avgGlu1DI = take the average of DI at each time point of all 1mM glutamate trials
# avgGlu3DI = take the average of DI at each time point of all 3mM glutamate trials
# avgGlu5DI = take the average of DI at each time point of all 5mM glutamate trials 

# avgXA1DI = take the average of DI at each time point of all 1mM xanthurenic acid trials 
# avgXA3DI = take the average of DI at each time point of all 3mM xanthurenic acid trials 
# avgXA10DI = take the average of DI at each time point of all 10mM xanthurenic acid trials 

# Time control vs. Glutamate
# Plot avgTCDI (x = time in minutes, y = instantaneous frequency (%baseline))
# Add error bars of time control
# lines for avgGlu1DI, avgGlu3DI, avgGlu5DI
# Add error bars of each dose

```

## Including scatterplots for peak FST and DI 

Here, I want to plot the maxiumum values of each trial of each dose/condition. I want two graphs, one comparing control to the different 
doses of glutamate and the other comparing to xanthurenic acid. Error bars should be included per dose/condition, as well as different 
colors to show distinuction. 

```{r plotSC}
##### Plot FST #####

# Extract maximum points per trial per condition and put them on a scatterplot with the values 'jittered'.
# Definitely need a for loop to make this process simplier.
# Include error bars for each condition 
# Repeat for DI
# Four scatter plots:
#     1. FST TC vs Glu (1, 3, 5 mM)
#     2. FST TC vs XA (1, 3, 10 mM)
#     3. DI TC vs Glu (1, 3, 5 mM)
#     4. DI TC vs XA (1, 3, 10 mM)

```

## Statistics 

TENTATIVE
Maximum changes in FST and DI compared by condition or responder using a One-Way ANOVA with Dunnett post-hoc. Average over time analyses were compared using a repeated measure with time as the within-subjects variable and condition as the between-subjects factor with Tukey post-hoc.  

