---
title: "KimThan_HW3"
author: "Kimberly Than"
date: "September 20, 2017"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE, fig.align="center")
```

## Objective
The goal is to subset a certain class of job title (Athletic Trainer) into a new data frame, and generate boxplots showing the distribution 
for the different classes of Althletic Trainer (I, II, and Head).

## Setting the working directory 

RStudio defaults to the .Rmd file's directory as the working directory, so it is not necessary to set your working directory when using 
RStudio go generate a Word or HTML document from this .Rmd file. 

## Importing data 

Next, I will import my data file of interest. Since the working directory used by RStudio (where this .Rmd file is located) is a sub-directory 
of my main directory `255E`, I need to use the `../data/` syntax to get to my `data` folder.

```{r importData}
CSU = read.csv("../data/california-state-university-2015.csv")
```

## Searching for the different classes

Since this data file contains numerous job titles, I want to find the different classes of Althletic Trainer. I will be using the ones under
a 12 month contract.

```{r findClasses}
jobs = levels(CSU$Job.Title)
jobs[grep(pattern = "ATHLETIC TRAINER", x = jobs)]
```

## Subsetting the different classes

Here I am subsetting out the three classes of althletic trainer.

``` {r subset}
AT1 = subset(CSU, Job.Title == "ATHLETIC TRAINER I - 12 MONTH")
AT2 = subset(CSU, Job.Title == "ATHLETIC TRAINER II - 12 MONTH")
AT3 = subset(CSU, Job.Title == "HEAD ATHLETIC TRAINER - 12 MONTH")
``` 

## Merging the subsets

Then, I am merging the three subsets into one data set.

``` {r mergeSubsets}
ATAll = rbind(AT1, AT2, AT3)
```

## Organizing the levels

The data set now only has the job titles I am interesetd in, with three levels in the order that I want to have them displayed.

```{r levels}
ATAll$Job.Title = factor(ATAll$Job.Title, 
                         levels = c("ATHLETIC TRAINER I - 12 MONTH", 
                                    "ATHLETIC TRAINER II - 12 MONTH",
                                    "HEAD ATHLETIC TRAINER - 12 MONTH" ))
```

## Including plots

Now we can make 3 boxplots, each representing the distribution of salary for each class. I abbreviated the name, specified the color for each
class, and included axes titles.

```{r boxplot, fig.cap="Boxplot of CSU salary distribution of three different classes of Athletic trainer in 2015."}
boxplot(Base.Pay~Job.Title, data = ATAll, names = c("AT I", "AT II", "Head AT"), 
        main = "CSU Athletic Trainer (AT) Base Pay in 2015",
        xlab = "Job Title", 
        ylab = "Base Pay (USD)",
        col = c("light blue1", "skyblue", "steelblue"))
```

## Including R results

We can use the aggregate function to calculate the mean base pay of each level of Athletic Trainer.

``` {r calculations}
mymeans = aggregate(Base.Pay~Job.Title, data = ATAll, FUN = mean)
mymeans
```

The function `kable` can also be used to make a table outside of the data frame.

```{r meansTable, results='asis'}
kable(mymeans, caption = "Mean base pay for each job level.")
```
