---
title: "KimThan_HW7"
author: "Kimberly Than"
date: "October 9, 2017"
output: word_document
---

```{r setup, include=FALSE, cache=TRUE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
```

```{r importData}
CSU = read.csv("../data/california-state-university-2015.csv")
CSU$Employee.Name = as.character(CSU$Employee.Name)
```

## Problem 1
Find all entries with name "Martinez".

```{r findMartinez}
CSU$Employee.Name[grepl(pattern = 'Martinez', CSU$Employee.Name)]
```

## Problem 2
Find everyone whose name starts with the letter "Wil".

```{r findWil}
CSU$Employee.Name[grepl(pattern = '^Wil', CSU$Employee.Name)]
```

## Problem 3
Find everyone with a hyphenated name (i.e. William-Sonoma).

```{r findHyphen}
hyphen_pattern = '[[:alpha:]]-[[:alpha:]]'
CSU$Employee.Name[grepl(hyphen_pattern, CSU$Employee.Name)]
```

## Problem 4
Find everyone whose middle name is 'Paul' (i.e. Matthew Paul Mark). 
```{r findMiddle}
middle_pattern = '[[:blank:]]Paul\\b'
CSU$Employee.Name[grepl(middle_pattern, CSU$Employee.Name)]
```

## Problem 5
Find all people with the last name 'Martinez'. 

```{r findLast}
CSU$Employee.Name[grepl(pattern = 'Martinez$', CSU$Employee.Name)]
```

## Problem 6
Find all people with the last name 'Martinez' (but no hyphenated names, no Jr.).

```{r findLast2}
CSU$Employee.Name[grepl(pattern = '[[:blank:]]Martinez$', CSU$Employee.Name)]
```

## Problem 7
Find all whose first name starts with 'E', has a middle initial, and last name is 'Martinez' (i.e. Eddie Martinez).
```{r findE}
length(grep('(^E)(.*\\s.\\s)(.*?Martinez$)', CSU$Employee.Name, perl = TRUE, value = TRUE))
grep('(^E)(.*\\s.\\s)(.*?Martinez$)', CSU$Employee.Name, perl = TRUE, value = TRUE)
```

## Problem 8
Find all whose first name starts with 'E', has NO middle initial, and last name is 'Martinez' (i.e. Edgar Martinez).
```{r findE}
grep('(^E)(?!.*\\s.\\s)(.*?Martinez$)', CSU$Employee.Name, perl = TRUE, value = TRUE)
```