---
title: "KimThan_HW8"
author: "Kimberly Than"
date: "October 17, 2017"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Importing data 

Here we are importing multiple .csv files and combining them into one large data frame. 
We are also using POSIX time to convert the x-axis to elapsed time in minutes. 

```{r importData}
fnames = dir("../data/temperature_trials", 
             pattern = "*.csv", full.names = TRUE)

for(i in 1: length(fnames) ){
  
  #open each file
  read.csv(fnames[i])
  temp = read.csv(fnames[i])
  # temp$TrialNumber = 
  temp$DateTime = as.POSIXct(temp$DateTime, origin = '1970-1-1', tz = "")
  temp$elapsedTime = difftime(temp$DateTime, temp$DateTime[1], units = 'mins')
  temp$elapsedTimeMin = as.numeric(temp$elapsedTime)
  
  #####
  # Grab the trial number
  loc = (regexpr(pattern ="Trial[0-9]*", text = fnames [i]))


  trialNumber = as.numeric(substr(fnames[i], start = loc[[1]][1]+5, 
       stop = loc[[1]][1] + attr(loc, 'match.length')-1))
  temp$trialNumber = trialNumber
  
  # rbind the new data in temp to the previous data in res
  if ( i == 1){
    res = temp
  } else {
    res = rbind( res, temp)
  }
}

res$POSIXt = as.POSIXct(res$POSIXt, origin = '1970-1-1', tz = "")
```

## Plotting first graph 

Here we are plotting all of the temperature data from channel TC0 for each trial. We plotted the first trial using plot() and then the 
rest of the trials using lines().

```{r plotRes}
firstTrial = 1
plot(x = res$elapsedTimeMin[res$trialNumber == firstTrial], 
     y = res$TC0[res$trialNumber == 1], 
     # TC0~elapsedTime, data = res[res$trialNumber == firstTrial]
     type = 'l',
     xlab = 'Elapsed Time, minutes',
     ylab = 'Temperature, C', 
     las = 1,
     xlim = c(min(res$elapsedTimeMin), max(res$elapsedTimeMin)), 
     ylim = c(min(res$TC0), max(res$TC0)),
     main = 'Channel TC0 for each Trial')

mtext(text = 'Channel TC0 for each Trial', side = 3, line = 2, cex = 1.5, adj = 0)

trialNums = unique(res$trialNumber)
for (y in 2:length(trialNums)){
  lines(x = res$elapsedTimeMin[res$trialNumber == trialNums[y]],
        y = res$TC0[res$trialNumber == trialNums[y]],
        col = y)  
}
```

## Importing Mussel Information 

Here we importing heating information that holds the information of the location ln50 for each trial.

```{r importMussel Info}
library(xlsx)
# info = read.xlsx("../data/Mussel_info.xlsx", sheetIndex = 1)

heatingInfo = read.xlsx("../data/Heating_trial_info.xlsx", sheetIndex = 1)
heatingInfo$TCchannel = as.character(heatingInfo$TCchannel)

for (x in 1:nrow(heatingInfo)){
  if (heatingInfo$TCLocation[x] == "In50") {
    chloc = regexpr(pattern = "[[:digit:]]", heatingInfo$TCchannel[2])
    chNum = substr(heatingInfo$TCchannel[1], 
               start = chloc[1][1],
               stop = chloc[1][1])
    chName = paste("TC", chNum, sep = "")
    trialNumber = heatingInfo$TrialNumber[x]
    
    temps = res[res$trialNumber == trialNumber ,chName]
    times = res$elapsedTimeMin[res$trialNumber == trialNumber]
    # res$chName[res$trialNumber == trialNumber] # won't work 
  }
}
```

```{r plotRes2}
plot(x = times,
     y = temps,
     type = 'l',
     xlab = 'Elapsed Time, minutes',
     ylab = 'Temperature, C',
     xlim = c(0, max(times)),
     ylim = c(min(temps), max(temps)))

     
```
